Software Citation Principles

### 2016-04-05 sc-principles/software-citation-principles.tex
changes from during call

\katznote{consider changing the language in the principles to be more
requirements-like -- e.g. use ``shall'' a lot; related: consider making the
principles machine-readable (has implications on language}

@@

software that was cited should be included in the metadata of the citing work, for example in the reference list of a journal article

@@

As the process of science has become increasingly digital, scientific outputs
and products have grown beyond simply papers and books to include software,
data, and other electronic components such as presentation slides, posters, 
(interactive)  graphs, maps, websites (e.g., blogs and forums),  multimedia 
(e.g., audio and  video lectures).  Scientific knowledge is embedded in these
components. And papers and books themselves are also becoming increasingly
digital, allowing them to become executable and reproducible. As we move towards
this future where science is performed in and recorded as a variety of linked
digital products, the characteristics and properties that developed for books
and papers need to be applied to all digital products and possibly adjusted.
Here, we are concerned specifically with the citation of software products. The
challenge is not just the textual citation of software in a paper, but the more
general identification of software used within the research process.

@@

\katznote{please check to make sure these are all still right}

@@

>>>>

%\katznote{consider changing the language in the principles to be more
%requirements-like -- e.g. use ``shall'' a lot; related: consider making the
%principles machine-readable (has implications on language}

@@

@@

As the process of science has become increasingly digital, scientific outputs
and products have grown beyond simply papers and books to include software,
data, and other electronic components such as presentation slides, posters, 
(interactive)  graphs, maps, websites (e.g., blogs and forums), and multimedia 
(e.g., audio and  video lectures).  Scientific knowledge is embedded in these
components. And papers and books themselves are also becoming increasingly
digital, allowing them to become executable and reproducible. As we move towards
this future where science is performed in and recorded as a variety of linked
digital products, the characteristics and properties that developed for books
and papers need to be applied to all digital products and possibly adjusted.
Here, we are concerned specifically with the citation of software products. The
challenge is not just the textual citation of software in a paper, but the more
general identification of software used within the research process.

@@

@@

Jed Brown, University of Colorado Boulder
